Title Goes Here

### 2020-05-05 analysis/paper/paper.Rmd
Chuck out the plots

Reading tps data and phase information of each artifact 
```{r}
#reading landmarks in tps, code from https://gist.github.com/mrdwab/2062329

@@

Make a plot for CV by site
```{r}
cv_plot_site <- cv_by_site_df_unnest %>% 
  select(-data)

@@

```{r}
cv_plot_site %>% 
pivot_longer(cols = -sitename, names_to = "group") %>% 
ggplot(aes(x = sitename, y = value, fill = as.factor(group))) + 
geom_bar(stat="identity", position=position_dodge())

```
Unlike the previous plot, in this one, the bars represent different attributes. You can see that SC has highest CV values of most attributes. Overall, SW values are very high.

@@

p + labs(x= "Site", fill = "Attributes")
```

@@

Computing Pearson's correlation 
```{r}

#simpler way to calculate Correlataion, you can use
SCOR <- cor(DF)

#a scatterplot matrix of Correlation
ALL<-pairs(DF)

# correlation per phase
cor2 <- 
df_sitename %>% 
  filter(SPstage.Stage == 2) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  cor(.)

ACOR2 <- pairs(cor2)

cor3 <- 
df_sitename %>% 
  filter(SPstage.Stage == 3) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  cor(.)

ACOR3 <- pairs(cor3)

# Plot for SCOR
library(corrplot)

par(mfrow=c(1,3))
# correlation for all
cplotall <- corrplot(SCOR, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45, main = "Correlatoin for ALL")
# for phase 2
cplot2 <- corrplot(cor2, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45, main = "Correlatoin for Phase 2")
# for phase 3
cplot3 <- corrplot(cor3, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45, main = "Correlatoin for Phase 3")

```
=> We may need to delete this chunk since we made new plots below using corrr package and same dataset.

@@

correlate(DF) %>% 
  network_plot()

@@

correlate(DF2) %>% 
  network_plot()

@@

correlate(DF3) %>% 
  network_plot()

### three phases at once
library(patchwork)
call + ctwo + cthree + plot_layout(ncol=1)
```
When it comes to the correlations between seven attributes, BL-ML, TW-MW, TL-TW, and TL-SL are relatively close to each other. There is no negative correlation among the attributes. Compared to the 2nd phase, in 3rd phase, correlations of SL with TW and MW, and TL with TWm SL, and MW get stronger. On the other hand, the correlation of TW-SW becomes weeker. Overall, the correlation between attributes became stronger from 2nd to 3rd phase.

@@

#simpler way to calculate Correlataion, you can use
SYG6_cor <- cor(SYG6_DF)

#a scatterplot matrix of Correlation
pairs(SYG6_DF)

cplot_SYG6 <- corrplot(SYG6_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

@@

@@

#simpler way to calculate Correlataion, you can use
SYG1_2cor <- cor(SYG1_2DF)

#a scatterplot matrix of Correlation
pairs(SYG1_2DF)

cplot_SYG1_2 <- corrplot(SYG1_2cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

@@

@@

#simpler way to calculate Correlataion, you can use
SYG1_1cor <- cor(SYG1_1DF)

#a scatterplot matrix of Correlation
pairs(SYG1_1DF)

cplot_SYG1_1 <- corrplot(SYG1_1cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

@@

@@

Correlations for each site
```{r}
par(mfrow=c(1,3))
cplot_SYG6_ <- corrplot(SYG6_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45, title = "SYG6")
cplot_SYG1_1 <- corrplot(SYG1_1cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45, title = "SYG1_1")
cplot_SYG1_2 <- corrplot(SYG1_2cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45, title = "SYG1_2")

@@

```{r}
#I'm working on how to read oulines and how to use them for anlaysis. We may not use this for the research.
# reading landmarks and outline in tps, code from Morpho package, adjust readallTPS function.

#readalltps = function(file) 
{
   # out = list()
   # exOut <- FALSE
  # noutline <- 0
  # input <- readLines(file)
   # LM <- grep("LM=", input)
  # LMstring <- input[LM]
   # nLM <- sapply(LMstring, strsplit, split = "=")
  #  nLM <- unlist(nLM)
   # nLM <- as.integer(nLM[-which(nLM == "LM")])
  #  nobs <- length(nLM)
   # ID <- grep("ID=", input)
  #  IDstring <- input[ID]
   # nID <- sapply(IDstring, function(x) {
   #     x <- gsub("=", "_", x)
  #  })
   # nID <- gsub(" ", "", unlist(nID))
  #  out$ID <- nID
   # outline <- grep("CURVES=", input)
  #  if (length(outline) > 0) {
   #     exOut <- TRUE
    #    outlinestring <- input[outline]
     #   noutline <- sapply(outlinestring, strsplit, split = "=")
      #  noutline <- unlist(noutline)
      #  noutline <- as.integer(noutline[-which(noutline == "CURVES")])
    #    LMoutline <- (sapply(outline, function(x) {
   #         x <- max(which(LM < x))  })) }
 #   LMdata <- list()
  #  for (i in 1:nobs) {
  #      if (nLM[i] > 0) {
   #         LMdata[[i]] <- as.numeric(unlist(strsplit(unlist(input[c((LM[i] + 
      #          1):(LM[i] + nLM[i]))]), split = " ")))
       #     LMdata[[i]] <- matrix(LMdata[[i]], nLM[i], 2, byrow = TRUE)
        }
   #     else LMdata[[i]] <- NA }
   # names(LMdata) <- nID
  #  out$LM <- LMdata
   # if (exOut) {
    #    outlineData <- list()
     #   for (i in 1:nobs) {
      #      if (i %in% LMoutline) {
       #         i1 <- grep(i, LMoutline)
        #        outlinetmp <- list()
         #       ptr <- outline[i1] + 1
          #      j <- 1
           #     while (j <= noutline[i1]) {
            #      tmpnr <- as.integer(unlist(strsplit(input[ptr], 
        #            split = "="))[2])
         #         outlinetmp[[j]] <- matrix(as.numeric(unlist(strsplit(input[(ptr + 
         #           1):(ptr + tmpnr)], split = " "))), tmpnr, 
          #          2, byrow = TRUE)
           #       ptr <- ptr + tmpnr + 1
            #      j <- j + 1  }
             #   outlineData[[i]] <- outlinetmp  }
          #  else outlineData[[i]] <- NA }
       # names(outlineData) <- nID
      #  out$outlines <- outlineData }
 #   cat(paste("Read", nobs, "datasets with", sum(noutline), "outlines\n"))
#    return(out)}

#try to read all data(landmarks and outlines) from one file
# lm_trial <- readalltps(here("analysis/data/raw_data/A_BG_2.tps"))

#read all files from raw_data
# tps_files <- list.files(here("analysis/data/raw_data"), full.names = TRUE)
# lm_landmarks <- map(tps_files, readalltps)
# names(lm_landmarks) <- list.files(here("analysis/data/raw_data"))

#lm_landmarks = c()
#for (i in 1:length(files)) {
#  filename <- paste(datadir, files[i], sep = "")
 # print(filename)
#  landmarks <- readalltps(filename)
# lm_landmarks <- c(lm_landmarks, landmarks)}

>>>>

Reading tps data and phase information of each artifact 
```{r, echo = FALSE}
#reading landmarks in tps, code from https://gist.github.com/mrdwab/2062329

@@

cv_plot_site <- cv_by_site_df_unnest %>% 
  select(-data)

@@

@@

p + labs(x= "Site", fill = "Attributes")
```
Unlike the previous plot, in this one, the bars represent different attributes. You can see that SC has highest CV values of most attributes. Overall, SW values are very high.

@@

@@

direction_all <- correlate(DF) %>% 
  network_plot()

@@

direction_2 <- correlate(DF2) %>% 
  network_plot()

@@

direction_3 <-correlate(DF3) %>% 
  network_plot()

### three phases at once
library(patchwork)
call + ctwo + cthree + plot_layout(ncol=1)

direction_all+ direction_2 + direction_3 + plot_layout(ncol=1)
```
When it comes to the correlations between seven attributes, BL-ML, TW-MW, TL-TW, and TL-SL are relatively close to each other. There is no negative correlation among the attributes. Compared to the 2nd phase, in 3rd phase, correlations of SL with TW and MW, and TL with TWm SL, and MW get stronger. On the other hand, the correlation of TW-SW becomes weeker. Overall, the correlation between attributes became stronger from 2nd to 3rd phase.

@@

@@

SYG6_cor <- cor(SYG6_DF)

@@

@@

SYG1_2cor <- cor(SYG1_2DF)

@@

@@

SYG1_1cor <- cor(SYG1_1DF)

@@

Correlations for each site
```{r}

@@
